Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-04-29 thesis/paper/thesis.tex
Asdsa
hi

\subsection{Research Questions} \label{rqs}
\begin{description}
\item[\textbf{RQ1:}] What drives API evolution?
\item[\textbf{RQ2:}] To what extent can we reverse engineer API change decisions?
\end{description}

%Structure of the paper
The sections following the Introduction are structured as follows: In Section \ref{existing_literature}, we present the existing literature related to our study. Section \ref{case_company_description} describes the case company and how it was selected. A description of our methodology is introduced in Section \ref{methodology}. In Section \ref{results}, the results of our study are presented, and in Section \ref{conclusion}, we discuss the findings of our study.

@@

%%Lehman's laws (!!!improve later)
An early study made in the area of software evolution suggests that changes to software must obey one of eight laws of software evolution \cite{lehman1980programs}. The laws presented in the study are 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conversation of Familiarities, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}. The study also outlines that these laws only apply to E-programs, which are programs that are ``change prone" and that ``mechanise a human or societal activity".

@@

%Reasons for choosing case study
The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context. The applicability of case studies in such scenarios is supported by existing studies \cite{benbasat1987case} \cite{runeson2009guidelines} \cite{yin2013case} \cite{robson2002real}. An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}. An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change, and that input from the industry is vital to the success of the research; especially to be able to answer \textbf{RQ2}.

>>>>

\subsection{Research Questions} \label{rqs}
\begin{description}
\item[\textbf{RQ1:}] What drives API evolution?x
\item[\textbf{RQ2:}] To what extent can we reverse engineer API change decisions?
\end{description}

%Structure of the paper
The sections following the Introduction are structured as follows: In Section \ref{existing_literature}, we present the background and previously published work that is related to our study. Section \ref{case_company_description} describes the case company and how it was selected. A description of our methodology is introduced in Section \ref{methodology}. In Section \ref{results}, the results of our study are presented, and in Section \ref{conclusion}, we discuss the findings of our study.

@@

%%Lehman's laws (!!!improve later)
An early study made in the area of software evolution suggests that changes to software must obey one of eight laws of software evolution \cite{lehman1980programs}. The laws presented in the study are 1) Continuing Change, 2) Increasing Complexity, 3) Self Regulation, 4) Conservation of Organisational Stability, 5) Conversation of Familiarities, 6) Continuing Growth, 7) Declining Quality and 8) Feedback System \cite{lehman1980programs}. The study also outlines that these laws only apply to E-programs, which are programs that are ``change prone" and that ``mechanise a human or societal activity" \cite{lehman1980programs}.o

@@

%Reasons for choosing case study
The reason the selected methodology was used is that it is essential to study the phenomenon of API change in its natural context. The applicability of case studies in such scenarios is supported by existing literature \cite{benbasat1987case} \cite{runeson2009guidelines} \cite{yin2013case} \cite{robson2002real}. An alternative approach that was considered was design research, but if a prototype API was to be used instead of one which is tried and tested in an industry setting, the study would lack real-life context \cite{runeson2009guidelines}. An additional motivation for why the case study approach was used is that there is little existing research conducted in the area of motives behind API change, and that input from the industry is vital to the success of the research; especially to be able to answer \textbf{RQ2}.
